### 2020-04-30 README.Rmd
use method argument not model FFS

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
set.seed(42)
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```

>>>>

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
set.seed(42)
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, method = "REML")
draw(m)
```
